\documentclass{article}
\usepackage{longtable}
\usepackage{hyperref}

\title{Software Requirements Specification\\Final Project}
\author{Elvis Montiel, David Montiel, Steven Mayorquin, Vincent Lozano}
\date{Snapshot 4}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Revision History}
\begin{longtable}{|p{2cm}|p{3cm}|p{8cm}|}
\hline
Version & Date & Description \\ \hline
1.0 & Snapshot 1 & Initial requirements document. \\ \hline
2.0 & Snapshot 2 & Added memory creation and memory template requirements. \\ \hline
3.0 & Snapshot 3 & Added contact management and search/filter requirements. \\ \hline
4.0 & Snapshot 4 & Finalized requirements for the complete simulated system including reminder and settings planning. \\ \hline
\end{longtable}

\section{Introduction}
\subsection{Purpose}
This document describes the simulated requirements for an application based on Want2Remember from the ascent website.

\subsection{Product Scope}
The simulated system helps users create, organize, search, and view memories, reminders, tasks, and contacts.

\section{External Interface Requirements}
\subsection{User Interface}
The system shall include a home page, login page, memory page, create memory page, contacts page, search page, and settings page.

\subsection{Software Interfaces}
The simulated system shall use React, React Native, Firebase Authentication, Firestore-style storage, Jira, TestRail, Docker Compose, and GitHub.

\section{Functional Requirements}
\begin{longtable}{|p{3cm}|p{10cm}|}
\hline
Requirement ID & Requirement \\ \hline
FR-1 & The system shall allow users to log in. \\ \hline
FR-2 & The system shall allow users to view saved memories. \\ \hline
FR-3 & The system shall allow users to create new memory entries. \\ \hline
FR-4 & The system shall allow users to view contacts. \\ \hline
FR-5 & The system shall allow users to search stored information. \\ \hline
FR-6 & The system shall allow users to start creating a new memory entry. \\ \hline
FR-7 & The system shall allow users to select a memory template before creating a memory. \\ \hline
FR-8 & The system shall provide template options for appointments, medication notes, tasks, contacts, passwords, and custom notes. \\ \hline
FR-9 & The system shall allow users to save a completed memory entry. \\ \hline
FR-10 & The system shall organize saved memories by category or template type. \\ \hline
FR-11 & The system shall allow users to view saved contacts. \\ \hline
FR-12 & The system shall allow users to create a simulated contact entry. \\ \hline
FR-13 & The system shall allow users to link a memory to a contact. \\ \hline
FR-14 & The system shall allow users to search saved memories by keyword. \\ \hline
FR-15 & The system shall allow users to filter saved memories by category, date, contact, or template type. \\ \hline
FR-16 & The system shall allow users to view memories related to a selected contact. \\ \hline
FR-17 & The system shall allow users to view planned reminder information connected to saved memories. \\ \hline
FR-18 & The system shall allow users to view or update simulated account settings and reminder preferences. \\ \hline
FR-19 & The system shall support a workflow that connects login, memory creation, contacts, search, filters, and reminders. \\ \hline
FR-20 & The system shall maintain the practice simulation disclaimer in project documentation. \\ \hline
\end{longtable}

\section{Nonfunctional Requirements}
\begin{longtable}{|p{3cm}|p{10cm}|}
\hline
Requirement ID & Requirement \\ \hline
NFR-1 & The documentation shall clearly state that the repository is a practice simulation and not a working production application. \\ \hline
NFR-2 & The planned design should consider ease of use for users who may need memory support. \\ \hline
NFR-3 & The planned design should consider privacy for stored memory and contact information. \\ \hline
NFR-4 & The documentation should remain organized and consistent across snapshots. \\ \hline
\end{longtable}

\section{Legal and Ethical Considerations}
The simulated system may involve sensitive personal information. The design should consider privacy, consent, secure storage, and responsible handling of user data.

\subsection{Snapshot 2 Privacy Update}

Memory entries may contain sensitive personal information. The simulated system should consider privacy, user consent, secure authentication, and restricted access to saved memories.

\subsection{Snapshot 3 Privacy Update}

Contact information may include sensitive personal details such as names, phone numbers, email addresses, relationships, and notes. The simulated system should protect contact data, limit access to the signed-in user, and avoid exposing private information without consent.

\subsection{Snapshot 4 Privacy Update}

Reminder information, account settings, and linked personal data may reveal sensitive daily habits and personal relationships. The simulated system should consider secure handling of reminder data, limited account access, and careful documentation of how private information would be protected in a real implementation.

\section{Glossary}
\begin{longtable}{|p{3cm}|p{10cm}|}
\hline
Term & Meaning \\ \hline
SRS & Software Requirements Specification \\ \hline
FR & Functional Requirement \\ \hline
NFR & Nonfunctional Requirement \\ \hline
\end{longtable}

\end{document}