\documentclass{article}
\usepackage{longtable}
\usepackage{hyperref}

\title{Software Requirements Specification\\Final Project}
\author{Elvis Montiel, David Montiel, Steven Mayorquin, Vincent Lozano}
\date{Snapshot 3}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Revision History}
\begin{longtable}{|p{2cm}|p{3cm}|p{8cm}|}
\hline
Version & Date & Description \\ \hline
1.0 & Snapshot 1 & Initial requirements document. \\ \hline
2.0 & Snapshot 2 & Added memory creation and memory template requirements. \\ \hline
3.0 & Snapshot 3 & Added contact management and search/filter requirements. \\ \hline
\end{longtable}

\section{Introduction}
\subsection{Purpose}
This document describes the simulated requirements for an application based on Want2Remember from the ascent website.

\subsection{Product Scope}
The simulated system helps users create, organize, search, and view memories, reminders, tasks, and contacts.

\section{External Interface Requirements}
\subsection{User Interface}
The system shall include a home page, login page, memory page, create memory page, contacts page, and search page.

\subsection{Software Interfaces}
The simulated system shall use React, React Native, Firebase Authentication, Firestore-style storage, Jira, TestRail, Docker Compose, and GitHub.

\section{Functional Requirements}
\begin{longtable}{|p{3cm}|p{10cm}|}
\hline
Requirement ID & Requirement \\ \hline
FR-1 & The system shall allow users to log in. \\ \hline
FR-2 & The system shall allow users to view saved memories. \\ \hline
FR-3 & The system shall allow users to create new memory entries. \\ \hline
FR-4 & The system shall allow users to view contacts. \\ \hline
FR-5 & The system shall allow users to search stored information. \\ \hline
FR-6 & The system shall allow users to start creating a new memory entry. \\ \hline
FR-7 & The system shall allow users to select a memory template before creating a memory. \\ \hline
FR-8 & The system shall provide template options for appointments, medication notes, tasks, contacts, passwords, and custom notes. \\ \hline
FR-9 & The system shall allow users to save a completed memory entry. \\ \hline
FR-10 & The system shall organize saved memories by category or template type. \\ \hline
FR-11 & The system shall allow users to view saved contacts. \\ \hline
FR-12 & The system shall allow users to create a simulated contact entry. \\ \hline
FR-13 & The system shall allow users to link a memory to a contact. \\ \hline
FR-14 & The system shall allow users to search saved memories by keyword. \\ \hline
FR-15 & The system shall allow users to filter saved memories by category, date, contact, or template type. \\ \hline
FR-16 & The system shall allow users to view memories related to a selected contact. \\ \hline
\end{longtable}

\section{Legal and Ethical Considerations}
The simulated system may involve sensitive personal information. The design should consider privacy, consent, secure storage, and responsible handling of user data.

\subsection{Snapshot 2 Privacy Update}

Memory entries may contain sensitive personal information. The simulated system should consider privacy, user consent, secure authentication, and restricted access to saved memories.

\subsection{Snapshot 3 Privacy Update}

Contact information may include sensitive personal details such as names, phone numbers, email addresses, relationships, and notes. The simulated system should protect contact data, limit access to the signed-in user, and avoid exposing private information without consent.

\section{Glossary}
\begin{longtable}{|p{3cm}|p{10cm}|}
\hline
Term & Meaning \\ \hline
SRS & Software Requirements Specification \\ \hline
FR & Functional Requirement \\ \hline
\end{longtable}

\end{document}