\documentclass{article}

\title{Snapshot Objectives\\Final Project}
\author{Elvis Montiel, David Montiel, Steven Mayorquin, Vincent Lozano}
\date{Snapshot 4}

\begin{document}
\maketitle

\section{Snapshot 1: Start}

The goal of Snapshot 1 is to establish the beginning of the simulated Want2Remember project. This includes creating the GitHub repository structure, adding the required practice simulation disclaimer, creating the initial README, creating the first SDD and SRS documents, creating the Docker Compose service plan, setting up Jira tasks and bugs, and adding initial TestRail reports.

\section{Snapshot 2: Checkpoint 1}

The goal of Snapshot 2 is to simulate the first major feature of the project: memory creation and memory templates. This snapshot builds on the initial project setup from Snapshot 1 by adding requirements, design details, user instructions, Jira tasks, bugs, and TestRail test cases for the memory creation workflow.

\subsection{Snapshot 2 Objectives}

The objectives for Snapshot 2 are to define the memory creation workflow, document memory template options, update the Software Design Document, update the Software Requirements Specification, update the Design Specification, update the User Manual, create new Jira tasks and bugs, and create a Snapshot 2 TestRail report.

\subsection{Snapshot 1 Reflection}

Snapshot 1 completed the initial repository structure, project disclaimer, README, initial SDD, initial SRS, design spec, user manual, Docker Compose service plan, Jira setup, and TestRail setup. The main remaining item from Snapshot 1 is the workflow diagram, which will be added or finalized in a later snapshot.

\section{Snapshot 3: Checkpoint 2}

The goal of Snapshot 3 is to simulate adding contact management and search/filter functionality. This snapshot builds on Snapshot 2 by adding features that help users organize people connected to memories and locate saved information more easily.

\subsection{Snapshot 3 Objectives}

The objectives for Snapshot 3 are to define the contact management workflow, define the search/filter workflow, update the Software Design Document, update the Software Requirements Specification, update the Design Specification, update the User Manual, create new Jira tasks and bugs, and create a Snapshot 3 TestRail report.

\subsection{Snapshot 2 Reflection}

Snapshot 2 completed the simulated memory creation and memory template feature. The SDD, SRS, Design Spec, User Manual, Snapshot Objectives, Jira tasks, and TestRail report were updated for that feature. Snapshot 3 extends this work by adding contacts and search/filter planning.

\section{Snapshot 4: Final Checkpoint}

The goal of Snapshot 4 is to finalize the simulated project documentation, complete the overall planned system description, add final testing and reporting updates, complete the workflow diagram reference, and summarize future work for the project.

\subsection{Snapshot 4 Objectives}

The objectives for Snapshot 4 are to finalize all major project documents, summarize the full simulated feature set, confirm the complete planned workflow, add final documentation updates for reminders and settings, create final Jira tasks and risks, and create a final Snapshot 4 TestRail report.

\subsection{Snapshot 3 Reflection}

Snapshot 3 completed the simulated contacts and search/filter planning. The SDD, SRS, Design Spec, User Manual, and Snapshot Objectives were updated to describe how contacts connect to memories and how users may search and filter saved information. Snapshot 4 completes the project by consolidating all work into a final documented version.

\subsection{Final Project Reflection}

Across all snapshots, the simulated project established repository planning, documentation structure, feature planning, testing reports, Jira planning, and Docker service planning. The final snapshot presents a complete simulation of a memory-support application design with memory creation, templates, contacts, search/filter support, reminder planning, and future improvement ideas.

\end{document}