\documentclass{article}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{hyperref}

\title{Software Design Document\\Final Project}
\author{Elvis Montiel}
\date{Snapshot 1}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Revision History}
\begin{longtable}{|p{2cm}|p{3cm}|p{8cm}|}
\hline
Version & Date & Description \\ \hline
1.0 & Snapshot 1 & Initial design document for the simulated project. \\ \hline
\end{longtable}

\section{Introduction}
\subsection{Purpose}
This document describes the simulated design of the final project for this course. The purpose of the simulated system is to organize memories, reminders, contacts, and daily information for users who need memory support.

\subsection{Intended Audience}
The intended audience includes the professor for this course and group members for this project.

\subsection{System Overview}
The simulated system contains a frontend interface, a mobile interface, Firebase-style authentication and storage, and documentation explaining how the system would be developed.

\section{System Architecture}
The planned architecture contains a React frontend, a React Native mobile interface, Firebase Authentication, and cloud storage.

\section{User Interface}
The initial simulated interface includes a home page, login page, memory list page, create memory page, contacts page, and search page.

\section{Database Explanation}
The simulated database stores users, memories, contacts, templates, reminders, and account settings.

\section{Glossary}
\begin{longtable}{|p{3cm}|p{10cm}|}
\hline
Term & Meaning \\ \hline
SDD & Software Design Document \\ \hline
SRS & Software Requirements Specification \\ \hline
UI & User Interface \\ \hline
Firebase & Simulated cloud backend and database service \\ \hline
\end{longtable}

\section{References}
Want2Remember senior design materials provided for class simulation.

\end{document}