\documentclass{article}
\usepackage{longtable}

\title{Design Specification\\Final Project}
\author{Elvis Montiel, David Montiel, Steven Mayorquin, Vincent Lozano}
\date{Snapshot 4}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Introduction}

This document describes the simulated design specification for the final project.

\section{Page Breakdown}

\begin{longtable}{|p{4cm}|p{9cm}|}
\hline
Page or Feature & Description \\ \hline
Home Page & Starting page for the simulated application. \\ \hline
Login Page & Allows a user to sign in using simulated authentication. \\ \hline
Memory List Page & Displays saved memories. \\ \hline
Contacts Page & Displays contacts connected to memories. \\ \hline
Contact Details Page & Displays full details for a selected contact and related memories. \\ \hline
Search Page & Allows the user to search stored information. \\ \hline
Filter Controls & Allows the user to narrow search results by category, date, contact, or template type. \\ \hline
Template Selection Page & Allows the user to choose a structured memory template. \\ \hline
Create Memory Page & Allows the user to enter and save memory information. \\ \hline
Settings Page & Allows the user to view or update simulated account preferences and reminder settings. \\ \hline
Reminder View & Displays planned reminder information connected to saved memories. \\ \hline
\end{longtable}

\section{Tool Breakdown}

\begin{longtable}{|p{4cm}|p{9cm}|}
\hline
Tool & Purpose \\ \hline
GitHub & Stores the repository and snapshot history. \\ \hline
Jira & Tracks simulated tasks, bugs, and project progress. \\ \hline
TestRail & Stores simulated test runs and reports. \\ \hline
Docker Compose & Describes planned services for the simulated application. \\ \hline
LaTeX & Used for formal project documentation. \\ \hline
Workflow Diagram & Describes the simulated structure and flow of the planned system. \\ \hline
\end{longtable}

\section{Simulated Dependencies}

The simulated project may use React, React Native, Firebase Authentication, Firestore-style storage, Docker, Docker Compose, Jira, TestRail, and GitHub.

\section{Docker Service Plan}

The Docker Compose file defines a planned frontend service and a planned Firebase emulator service.

\section{Data Design}

The simulated system may store users, memories, contacts, templates, reminders, and account settings.

\section{Snapshot 2 Design Update: Memory Creation Feature}

Snapshot 2 adds the simulated design for memory creation and memory templates.

\subsection{Create Memory Page}

The Create Memory page allows the user to begin creating a new memory entry. The page would include a title field, category selection, date field, notes field, and save button.

\subsection{Template Selection Page}

The Template Selection page allows the user to choose what type of memory they want to create. Planned templates include appointment, medication, task, contact-related memory, password entry, and custom note.

\subsection{Memory Template Fields}

\begin{longtable}{|p{4cm}|p{9cm}|}
\hline
Template & Planned Fields \\ \hline
Appointment & Title, date, time, location, notes \\ \hline
Medication & Medication name, dosage, time, instructions \\ \hline
Task & Task title, due date, priority, notes \\ \hline
Contact Memory & Contact name, relationship, phone number, notes \\ \hline
Password Entry & Account name, username, password hint, notes \\ \hline
Custom Note & Title, category, notes \\ \hline
\end{longtable}

\section{Snapshot 3 Design Update: Contacts and Search}

Snapshot 3 adds the simulated design for contact management and search/filter functionality.

\subsection{Contacts Page}

The Contacts page displays a list of saved contacts. Each contact may show the contact name, relationship, phone number, and a short note. The user may select a contact to view more information.

\subsection{Contact Details Page}

The Contact Details page displays the full information for one contact. This may include the contact name, relationship, phone number, email address, notes, and related memories.

\subsection{Search Page}

The Search page allows the user to search saved memories by keyword. Search results may include memory title, category, date, template type, and related contact.

\subsection{Filter Controls}

Filter controls allow the user to narrow saved memories by category, date, contact, or template type.

\subsection{Snapshot 3 Page and Feature Additions}

\begin{longtable}{|p{4cm}|p{9cm}|}
\hline
Page or Feature & Description \\ \hline
Contacts Page & Displays saved contacts connected to the user's memories. \\ \hline
Contact Details Page & Displays detailed information about a selected contact and related memories. \\ \hline
Search Page & Allows the user to search saved memories by keyword. \\ \hline
Filter Controls & Allows the user to filter memories by category, date, contact, or template type. \\ \hline
\end{longtable}

\section{Snapshot 4 Final Design Update}

Snapshot 4 finalizes the simulated project documentation by summarizing the complete planned feature set and overall system flow.

\subsection{Settings Page}

The Settings page allows the user to review or update simulated account preferences. Planned settings may include reminder preferences, account details, and display preferences.

\subsection{Reminder View}

The Reminder View displays planned reminder information associated with saved memories such as appointments, medications, and tasks. This section helps show how reminders would connect to stored memory data.

\subsection{Final Workflow Summary}

The final planned workflow begins when the user opens the application and signs in. The user may create memories, select templates, connect memories to contacts, search for saved information, apply filters, review related contact details, and view reminder-related information. The simulated design supports organization, retrieval, and review of important personal information.

\subsection{Final Design Summary Table}

\begin{longtable}{|p{4cm}|p{9cm}|}
\hline
Final Area & Summary \\ \hline
Memory Management & Users may create and save structured memories using templates. \\ \hline
Contact Management & Users may store contacts and connect them to memories. \\ \hline
Search and Filter & Users may search memories and narrow results using filters. \\ \hline
Reminder Planning & Users may review planned reminders associated with saved information. \\ \hline
Settings & Users may review simulated account and reminder preferences. \\ \hline
Documentation Completion & Snapshot 4 finalizes the simulated design documentation for the project. \\ \hline
\end{longtable}

\end{document}